\section{Introduction}

Finite element simulations of heterogeneous materials constructed using classical finite elements frequently have difficulty capturing the internal stress-strain behavior which can be a primary driving force in the overall material response. Of particular interest are the responses of highly heterogeneous materials such as polymer bonded crystalline materials which are comprised of a hard crystalline component bound in a polymeric matrix. These materials can be found in applications as varied as asphalt or plastic explosives.

Several approaches have been developed to address these concerns but few approach it with the generality of Eringen and Suhubi(~\cite{bib:eringen64} and \cite{bib:eringen64_2}) in their, theory of ``micromorphic,'' continuum mechanics. This approach holds the promise of passing information between simulations of the microscale on macroscale response through a straightforward coupling as well as the ability to develop constitutive models which can capture this response directly utilizing the micromorphic theory alone. The framework however requires specialized finite elements which are capable of handing the multi-field nature.

Such a finite element is proposed to be developed here which will prove foundational for the research into the development and calibration of higher order continuum models. While these models are beyond the scope of the efforts detailed here, the framework to utilize them is a significant part of the overall effort. A roubust, highly verified, and documented element would provide a very useful tool in the research effort.